% Chapter 7 Content - User Input and while Loops
% This file contains the content for Chapter 7 based on actual Python files

This document contains the essential keywords and definitions from Chapter 7 of "Python Crash Course" along with their corresponding code examples.

\subsection*{1. input() Function - User Input}
\textbf{Definition}: A function that pauses your program and waits for the user to enter some text, which is then stored as a string.

\lstinputlisting[language=Python, caption=Basic user input]{Chapter07/702_greeter.py}

\subsection*{2. while Loop - Conditional Repetition}
\textbf{Definition}: A loop that runs as long as, or while, a certain condition is true.

\lstinputlisting[language=Python, caption=while loop with user input]{Chapter07/701_parrot.py}

\subsection*{3. int() Function - String to Integer}
\textbf{Definition}: A function that converts a string containing a number to an integer.

\lstinputlisting[language=Python, caption=Converting string input to integer]{Chapter07/703_rollercoster.py}

\subsection*{4. Flag - Loop Control Variable}
\textbf{Definition}: A variable that acts as a signal to the program, often used to control while loops.

\begin{lstlisting}
active = True
while active:
    message = input("Enter 'quit' to end: ")
    if message == 'quit':
        active = False
    else:
        print(message)
\end{lstlisting}

\subsection*{5. break Statement - Immediate Exit}
\textbf{Definition}: A statement that immediately exits a loop without running any remaining code in the loop.

\begin{lstlisting}
while True:
    city = input("Enter a city name (or 'quit' to exit): ")
    if city == 'quit':
        break
    print(f"I'd love to go to {city.title()}!")
\end{lstlisting}

\subsection*{6. continue Statement - Skip Iteration}
\textbf{Definition}: A statement that skips the rest of the current iteration and returns to the beginning of the loop.

\begin{lstlisting}
current_number = 0
while current_number < 10:
    current_number += 1
    if current_number % 2 == 0:
        continue
    print(current_number)
\end{lstlisting}

\subsection*{7. Modulo Operator - \%}
\textbf{Definition}: An operator that divides one number by another and returns the remainder.

\begin{lstlisting}
number = 4 % 2  # 0 (even)
number = 5 % 2  # 1 (odd)
\end{lstlisting}

\subsection*{8. Moving Items Between Lists - List Operations}
\textbf{Definition}: The process of removing items from one list and adding them to another list.

\begin{lstlisting}
unconfirmed_users = ['alice', 'brian', 'candace']
confirmed_users = []

while unconfirmed_users:
    current_user = unconfirmed_users.pop()
    confirmed_users.append(current_user)
\end{lstlisting}

\subsection*{9. Removing All Instances - List Cleanup}
\textbf{Definition}: Removing all occurrences of a specific value from a list.

\begin{lstlisting}
pets = ['dog', 'cat', 'dog', 'goldfish', 'cat', 'rabbit', 'cat']
print(pets)

while 'cat' in pets:
    pets.remove('cat')

print(pets)
\end{lstlisting}

\subsection*{10. Filling Dictionary with User Input - Dynamic Data}
\textbf{Definition}: Building a dictionary by collecting user input in a loop.

\begin{lstlisting}
responses = {}
polling_active = True

while polling_active:
    name = input("\nWhat is your name? ")
    response = input("Which mountain would you like to climb someday? ")
    
    responses[name] = response
    
    repeat = input("Would you like to let another person respond? (yes/ no) ")
    if repeat == 'no':
        polling_active = False
\end{lstlisting}

\section*{Practical Examples from Chapter 7}

\subsection*{Working with User Input and Loops}
Chapter 7 introduces user input and while loops. Here are the key files:

\textbf{Basic User Input:}
\lstinputlisting[language=Python, caption=Chapter07/702\_greeter.py]{Chapter07/702_greeter.py}

\textbf{while Loops with User Input:}
\lstinputlisting[language=Python, caption=Chapter07/701\_parrot.py]{Chapter07/701_parrot.py}

\textbf{Numerical Input and Type Conversion:}
\lstinputlisting[language=Python, caption=Chapter07/703\_rollercoster.py]{Chapter07/703_rollercoster.py}

\textbf{To run these programs:}
\begin{verbatim}
python Chapter07/702_greeter.py
python Chapter07/701_parrot.py
python Chapter07/703_rollercoster.py
\end{verbatim}

\section*{Summary}
Chapter 7 focuses on user input and while loops. You learn how to get input from users, convert between data types, and create loops that run until a condition is met.

\section*{Key Takeaways}
\begin{itemize}
    \item input() gets user input as a string
    \item int() converts string to integer
    \item while loops run while condition is True
    \item Use flags to control while loops
    \item break exits a loop immediately
    \item continue skips to next iteration
    \item \% operator gives remainder
    \item Use while loops to move items between lists
    \item remove() removes first occurrence of value
    \item Build dictionaries with user input
    \item Always provide clear prompts to users
\end{itemize} 